Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2021-05-04 analysis/paper/asymsam.Rmd
Knitea

```{r setup, echo = FALSE,warning=FALSE, message = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = "",
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  cache.extra = 41,
  cache.path = "../cache/",
  collapse = TRUE,
  comment = "#>",
  dev = "pdf",
  # dpi = 300,
  out.extra = ""
)

@@

lons <- c(0, unique(pp_regr$lon), 360)
pp_regr %>%
  .[season == "Annual"] %>%
  .[, p.value := Pvaluate(estimate, std.error, df, "fdr"), by = .(season, term)] %>% 
  # Need to interpolate 0 and 360 to get closed contours
  qwrap(lon = c(1.25, 360 + 1.25) ~ c(-1.25, 360 + 1.25)) %>% 
  .[, lapply(.SD, function(x) approx(lon, x, xout = lons)$y), by = .(lat, season, term)] %>%
  ggplot(aes(lon, lat)) +
  geom_contour_fill(aes(z = estimate, fill = ..level..), 
                    breaks = breaks_pp) +
  stat_subset(aes(subset = is.na(estimate)), geom = "tile", color = "gray50") +
  geom_contour2(aes(z = p.value), breaks = 0.05) +
  geom_qmap(~.x[lat <= 10], keep = 0.015, weighting = 0.9) +
  scale_x_longitude(breaks = NULL) +
  scale_y_latitude(breaks = NULL, limits = c(-90, NA)) +
  discrete_scale("fill", "name", name = "Precipitation",
                 palette = discrete_div_pp,
                 guide = guide_colorsteps_bottom(show.limits = TRUE)) +
  scale_linetype(guide = "none") +
  coord_polar() +
  geom_coords() +
  # coord_quickmap(ylim = c(NA, 0)) +
  facet_grid(.~term, labeller = labeller(term = lab_sam)) +
  tag_facets("panel", position = "tl")  +
  no_grid 
```

>>>>

```{r setup, echo = FALSE,warning=FALSE, message = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = "",
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  cache.extra = 42,
  cache.path = "../cache/",
  collapse = TRUE,
  comment = "#>",
  dev = "pdf",
  # dpi = 300,
  out.extra = ""
)

@@

lons <- c(0, unique(pp_regr$lon), 360)
pp_regr %>%
  .[season == "Annual"] %>%
  .[, p.value := Pvaluate(estimate, std.error, df, "fdr"), by = .(season, term)] %>% 
  # Need to interpolate 0 and 360 to get closed contours
  qwrap(lon = c(1.25, 360 + 1.25) ~ c(-1.25, 360 + 1.25)) %>% 
  .[, lapply(.SD, function(x) approx(lon, x, xout = lons)$y), by = .(lat, season, term)] %>%
  ggplot(aes(lon, lat)) +
  geom_contour_fill(aes(z = estimate, fill = ..level..), 
                    breaks = breaks_pp) +
  stat_subset(aes(subset = is.na(estimate)), geom = "tile", color = "gray50") +
  geom_contour2(aes(z = p.value), breaks = 0.05, size = 0.2) +
  geom_qmap(~.x[lat <= 10], keep = 0.015, weighting = 0.9) +
  scale_x_longitude(breaks = NULL) +
  scale_y_latitude(breaks = NULL, limits = c(-90, NA)) +
  discrete_scale("fill", "name", name = "Precipitation",
                 palette = discrete_div_pp,
                 guide = guide_colorsteps_bottom(show.limits = TRUE)) +
  scale_linetype(guide = "none") +
  coord_polar() +
  geom_coords() +
  # coord_quickmap(ylim = c(NA, 0)) +
  facet_grid(.~term, labeller = labeller(term = lab_sam)) +
  tag_facets("panel", position = "tl")  +
  no_grid 
```
